\documentclass[]{report}
\usepackage{titlesec}

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{CompetitionRules/}{TeX_files/}}
\hypersetup{
	colorlinks=true, %set true if you want colored links
	linktoc=section,     %set to all if you want both sections and subsections linked
	linkcolor=black,  %choose some color if you want links to stand out
}
%reduce spacing above chapter title
\titlespacing*{\chapter}{0pt}{-50pt}{10pt}

\titleformat{\chapter}[display]
{\normalfont\bfseries}{}{0pt}{\Large}

\begin{document}



\chapter{Laboratory Session 1}
\section{Pre-Laboratory Report}
Complete this report before coming to the Laboratory Session

\begin{itemize}
	
	\item[\textbf{Due Date}]{Week of August 30th-September 3rd, \the\year \space in lab section. Submit report electronically before start of Lab via Blackboard (check assignments folder)}
	\item[\textbf{Subject}]{Section \#, FirstName LastName}
	\item[\textbf{Body}]{``I have read and will comply with the ECE 100 Course policies"}
	\item[\textbf{Short Answer Questions}]{
		\begin{enumerate}
			\item{What is a microprocessor? What is a microcontroller?}
			\item{What is the difference between a microprocessor and a microcontroller?}
			\item{Is an Arduino a microprocessor or microcontroller?}
		\end{enumerate}
	}
	\item[\textbf{Additional Task}]{Please complete Google Form attached at link below. Attach a screenshot of the “Response Sent” screen to verify completion. \href{https://docs.google.com/forms/d/1YDT2DtzWYms2BeuS1Wrks3ZANfYgNUmNhEl2PUm63Qc/prefill}{Google Form Link}}
	\item[\textbf{Additional Task}]{Bring Robot Kit to your lab section}
\end{itemize}

\section{Post-Laboratory Report}

\begin{itemize}
	\item[\textbf{Due Date}]{Week of September 6th-September 10th, \the\year \space in lab section. Submit report electronically before start of Lab via Blackboard (check assignments folder)}
	\item[\textbf{Contents}]{Please follow the template for Post-Laboratory Reports as given on Blackboard.}
\end{itemize}

\end{document}
