
\section{Competition 2 Rules}

\paragraph{Overview}The first robot competition will be a race against the clock. Your robot will be timed as it navigates a  simple maze. The team with the fastest run wins! 
The maze competition will test your robot's navigation skills via ultrasonic sensors. The key to a winning performance lies in your robot's obstacle avoidance algorithm. 


The competition rules are as follows:
\begin{enumerate}
	\item All angles will be 90 or 270 degrees, i.e., square corners. 
	\item Dead ends are possible. 
	\item The narrowest path will be 1 foot wide. 
	\item The overall outside dimensions of the maze will be approximately 4 feet by 8 feet.
	\item Your robot must start completely behind the starting line In fact, your robot will be positioned by the TA, facing forward at the starting line. 
	\item Your robot must finish completely beyond the finish line.
	\item Each team will run two trials. 
	\item The maximum time allowed per trial is 90 seconds. If your robot does not finish within 90 seconds, then its position will be recorded. 
	\item If no robot finishes the maze, then the robot which gets closest to the finish during its trials will be declared the winner. 
	\item You may then modify your robot in preparation for the second trial.
	\item In each laboratory section, the top team will be awarded bonus points (0.2*teamwork\_score) as described in the Lecture 1 slides. 
	\item The top team in each section will compete in a lecture runoff on the  Monday following the laboratory competitions. 
	
	
\end{enumerate}
Good luck!